%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins
\geometry{left=1.5cm, top=1.0cm, right=1.5cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Options: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%          awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Teague}{Beauchamp}
\position{Cybersecurity, Software Development {\enskip\cdotp\enskip} Computer Scientist}
\address{Logan, Utah, USA}

\mobile{+1 (435) 890-4084}
\email{beaurobby17@gmail.com}
\github{teague1toast1eater}
\linkedin{Teague-Beauchamp}

%-------------------------------------------------------------------------------
\begin{document}

  % Print the header with personal information
  \makecvheader[C]

  % Print the footer with page numbers
  \makecvfooter
    {\today}
    {Teague Beauchamp~~~·~~~Résumé}
    {\thepage}

  %-------------------------------------------------------------------------------
  % CV/RESUME CONTENT
  %-------------------------------------------------------------------------------

  %-------------------------------------------------------------------------------
  \cvsection{Education}
  %-------------------------------------------------------------------------------

  \begin{cventries}

    \cventry
      {B.S. in Computer Science}
      {Utah State University}
      {Logan, Utah}
      {Aug. 2021 - May. 2027}
      {
        \begin{cvitems}
          \item {Member of Free Software and Linux Club, participating in coding competitions and hackathons.}
          \item {Member of the Cybersecurity club, practicing ethical hacking and penetration testing skills.}
        \end{cvitems}
      }

  \end{cventries}

  %-------------------------------------------------------------------------------
  \cvsection{Skills}
  %-------------------------------------------------------------------------------

  \begin{cvskills}

    \cvskill
      {Code}
      {Python (Django, Flask, Tkinter, NumPy, Pandas, Matplotlib, PyTorch, PyTensor, Openpyxl, Poetry); C\# (Godot game development); Java (Gradle, Maven, JUnit); JavaScript (React), React Native, Vue, Next, Node, Express, Jest, Vite);  C++ (GCC/Clang); Rust; Bash/Zsh; PowerShell; HTML; CSS; x86 Asm; ARM Asm; R (statistical analysis).}

    \cvskill
      {Tools}
      {Git; GitHub (Secrets, Actions/Act, Copilot); GitLab; Vim; Neovim; JetBrains; Visual Studio; VS Code; Vitest; LaTeX (Overleaf, Pandoc); Markdown (Obsidian); UML (Lucidchart); Figma; Microsoft Office.}

    \cvskill
      {Data}
      {MySQL; PostgreSQL; SQLite; Azure SQL; Redis; JSON; YAML; TOML; XML; CSV.}

    \cvskill
      {Hosting}
      {Azure (App Service, Functions, AKS, DevOps, Storage); Docker (Hub, Compose, Networking, Volumes); Gunicorn; Nginx; Apache (HTTP, Kafka); SSH (OpenSSH); VMware; VirtualBox; Linux (Debian, Arch, systemd services \& timers, Ubuntu); MacOS (Homebrew); Windows (Windows Services, Task Scheduler, PowerShell).}

    \cvskill
      {Services}
      {Azure Active Directory; GitHub (API); GitLab (API); OAuth 2.0; Okta; OpenAPI; REST (JSON, HTTP verbs); Stripe.}
    
    \cvskill
      {Soft Skills}
      {Effective communication; Clean and organized code management; Problem-solving; Time management; Team collaboration; Adaptability; Attention to detail; Critical thinking; Leadership.}

  \end{cvskills}

  %-------------------------------------------------------------------------------
  \cvsection{Experience}
  %-------------------------------------------------------------------------------

  \begin{cventries}

    \cventry
      {Field Technician}
      {Jex Environmental Solutions}
      {Logan, Utah}
      {Sep. 2020 - Present}
      {
        \begin{cvitems}
          \item {Automating data analysis and log sorting on 10+ years of historical data using Python and R.}
          \item {Identify trends, and issues, to improve treatment processes.}
          \item {Troubleshooting, maintaining, and updating embedded systems to ensure reliable operation in remote locations used in alternative wastewater treatment solutions.}
          \item {Working under pressure to perform routine maintenance and emergency repairs on treatment systems, ensuring minimal downtime and compliance with environmental regulations.}
          \item {Communicating effectively with clients to explain technical issues and solutions in terms that can be understood by those unfamiliar with the equipment.}
          \item {Providing training on system operation and maintenance as needed.}
          \item {Documenting maintenance activities, repairs, and system performance to maintain accurate records for regulatory compliance and future reference.}
        \end{cvitems}
      }

    \cventry
      {Cabinet Builder}
      {Jensen's Custom Cabinets}
      {Providence, Utah}
      {Jan. 2020 - Sep. 2020}
      {
        \begin{cvitems}
          \item {Collaborated with team members to design and build custom cabinetry, ensuring high-quality craftsmanship and attention to detail.}
        \end{cvitems}
      }

    \cventry
      {Owner}
      {Mr.ChillMonkey}
      {Detroit, Michigan}
      {Apr. 2016 - Jan. 2020}
      {
        \begin{cvitems}
          \item {Founded and managed an online business specializing in custom longboard skateboards, overseeing all aspects from design to sales.}
          \item {Designed unique skateboard graphics and layouts using graphic design software, catering to customer preferences and trends.}
          \item {Worked with CNC machinery, and laser cutter/printer programs to produce high-quality longboard decks.}
          \item {Handled customer service, order fulfillment, and marketing efforts to grow the business and maintain a loyal customer base.}
        \end{cvitems}
      }

  \end{cventries}

  %-------------------------------------------------------------------------------

  \vspace*{\fill}
  \begin{center}
      \textbf{For more details, visit my LinkedIn.} \\
      \textbf{References available upon request.}
  \end{center}

  %-------------------------------------------------------------------------------
\end{document}
